\section{Appendix}

\subsection{Semi structured in-depth interview guide Interview Guide}\label{Interview guide}

\begin{enumerate}
    \item How do players react to and experience difficulty in video-games? 
    \item How do difficulty settings impact immersion and engagement? 
    \item What motivates players to persist through games they find difficult rather than quitting?
\end{enumerate}

\textbf{Introductory questions}
\begin{enumerate}
    \item What makes you define a game as difficult?
    \item Can you tell me how you generally feel about difficulty in video games?
\end{enumerate}

\textbf{Direct questions}
\begin{enumerate}
    \item Do you enjoy when a game is difficult and is challenging your abilities? Why?
    \item How do difficulty settings impact your enjoyment in a game?
    \begin{enumerate}
        \item How does it impact your engagement and immersion?
        \item Do you prefer games with fixed difficulty levels or adjustable difficulty settings? Why?
    \end{enumerate}
    \item Do you tend to go with the recommended setting or above/below?
    \item Have you ever quit a game because it was too difficult? Why or why not?
    \item Can you describe a time when a difficult game made you feel frustrated but still motivated to continue?
    \begin{enumerate}
        \item What made you motivated to continue?
    \end{enumerate}
    \item What role do in-game rewards (e.g., achievements, progression, story advancement) play in motivating you to push through challenges?
    \item Can you think of a game that was difficult, but not frustrating? What made it so?
\end{enumerate}

\textbf{Follow up questions}
\begin{enumerate}
    \item When you find something in a game frustrating, would you also consider that difficult?
    \item Do you think that the game should adjust its difficulty based on player performance or progress in the game?
    \item Do you think your personality has influence on how you experience and play video games? How?
    \begin{enumerate}
        \item Has overcoming challenges in games always been something you’ve felt the same way about, or has it evolved over time?
        \item Do you think that your willingness to overcome a challenge in a game reflects your willingness to overcome challenges in real life?
    \end{enumerate}
\end{enumerate}

\subsection{Interview Transcriptions}

